\title{AI-Driven Approaches for Network Resilience: From Attack-Defence Strategies to Cascading Failure Mitigation}
\author{Jordan~D.~~Lanct\^{o}t$^{1}$, Sean~P.~~Cornelius$^{1,2, \dagger}$}
\date{September 2024}

\maketitle
\thispagestyle{noNumber}

{\small
\begin{affiliations}
 \item \, Department of Physics, Toronto Metropolitan University, Toronto, ON M5B 2K3, Canada
 \item[$\dagger$] \, To whom correspondence should be addressed
\end{affiliations}
}

\vspace{3em}
\begin{abstract}
Networked systems, ubiquitous in modern infrastructure, are susceptible to cascading failures and targeted attacks. This research investigates network robustness through three interconnected studies. First, we explore the application of deep reinforcement learning (DRL) in network attack and defense scenarios. Neural network embedding frameworks are employed to discover vulnerable nodes, while DRL agents are developed to either dismantle networks efficiently or defend against such attacks through partial network concealment. Our early findings reveal a surprising disadvantage for defensive strategies across various network configurations.\\

Building on these insights, we will examine cascading failures using the Abelian sandpile model as a framework. We will simulate and analyze the efficacy of targeted interventions, including strategic sand dropping and link rewiring, to mitigate avalanche effects in networks. This approach will provide a deeper understanding of failure propagation dynamics and potential preventive measures.\\

Finally, we will extend our investigation of the Abelian sandpile model by applying DRL techniques to refine and optimize the aforementioned failure mitigation strategies. This advanced approach will aim to develop more sophisticated, adaptive methods for maintaining network integrity under diverse stress conditions. Through this comprehensive analysis of network vulnerabilities, failure mechanisms, and mitigation strategies, we will contribute fundamental insights into enhancing the robustness of complex networked systems, with potential applications spanning infrastructure protection and load management, communication networks, and cybersecurity.
\end{abstract}